Supplementary Material for Asymmetry paper

### 2020-05-14 Supplementary/Sup_mat.Rmd
model added to code

The second dataset is comprised of 60 participants who took part in a computerised version of this task. *more details*

@@

## Experiment 1: Hoop Size
```{r Load in Hoop size data, inclued = F, echo = F, cache=TRUE}
load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1")
load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1_draws")
```

>>>>

The second dataset is comprised of 60 participants who took part in a computerised version of this task. The task involved participants deciding where to place a virtual firetruck when there were two buildings which both had an equal chance of becoming the target for that trial. In this task, participants would decide where to place the firetruck and it would drive towards the target building. The speed at which the truck travelled was drawn from a uniform distribution of speeds within a specified range. This meant that the chance of success decrease linearly with distance from the target. This meant that the performance of the truck was very similar to participatns taking part in the _Throwing Task_, and thus the experiments were comparable. However, participants in this version of the task were much closer to using the optimal strategy than had been observed in previous versions of this task. Therefore, these data were used as a comparison for what to expect when participants were better able to use the optimal strategy.

@@

## Experiment 1: Hoop Size
```{r run model Hoop Size, include = F, echo = F, cache = TRUE}
# load model data 
load("../Analyses/Experiment_3_Hoop_size/data/model_data")

# get function for extracting draws 
source("extract_draws_functions/Hoop_size_draws.R")

# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
          data = model_data,
          family = "beta",
          prior = c(set_prior("student_t(3,0,3)", class = "b")),
          cores = 1,
          chains = 1,
          iter = 2000,
          warmup = 1000)

# extract draws 
draws <- HS_draw_post(Hoop_size_m1, model_data)
```

```{r Load in Hoop size data, include = F, echo = F, cache=TRUE}
# might not need this chunk
# load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1")
# load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1_draws")
```
